### 2025-11-18 CV3/CV.tex
CV-ru

\documentclass[a4paper,10pt]{article} % Default font size and paper size
%\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc}
\usepackage{fontspec} % For loading fonts

%\setmainfont{[Fontin-Regular.otf]}
\defaultfontfeatures{Mapping=tex-text}
% \setmainfont{[Fontin-Regular.otf]} % Main document font
% \setmainfont[SmallCapsFont = Fontin-SmallCaps.otf]{[Fontin-Regular.otf]} % Main document font
\setmainfont{Fontin-Regular.otf}[
  BoldFont       = Fontin-Bold.otf ,
  ItalicFont     = Fontin-Italic.otf ,
SmallCapsFont  = Fontin-SmallCaps.otf ]

\usepackage{xunicode,xltxtra,url,parskip} % Formatting packages

@@

\par{\centering{\Huge Dmitry Kovalev}\bigskip\par} % Your name

>>>>

\documentclass[a4paper,10pt]{article} % Default font size and paper size
\usepackage{fontspec} % For loading fonts

\defaultfontfeatures{Mapping=tex-text}

% \setmainfont{Fontin-Regular.otf}[
%   BoldFont       = Fontin-Bold.otf ,
%   ItalicFont     = Fontin-Italic.otf ,
% SmallCapsFont  = Fontin-SmallCaps.otf ]

\setmainfont{FontinSans_Cyrillic_R_46b.otf}[
  BoldFont       = FontinSans_Cyrillic_B_46b.otf,
  ItalicFont     = FontinSans_Cyrillic_I_46b.otf ,
  SmallCapsFont  = FontinSans_Cyrillic_SC_46b.otf
]
\usepackage{xunicode,xltxtra,url,parskip} % Formatting packages

@@

\par{\centering{\Huge Дмитрий Ковалев}\bigskip\par} % Your name

### 2025-11-18 CV3/awards.tex
CV-ru

\section{Honors and Awards}
\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
\begin{enumerate}
	\item  \textbf{CEMSE Student Research Excellence Award}, King Abdullah University of Science and Technology, 2021
	\item \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award at FL-ICML 2021 Workshop}}
	\item \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2021}, Yandex (highly selective: only 4 winners from Russia, Belarus, Kazakhstan)}
	\item {\bf  Annual PhD progress marked as Outstanding}, King Abdullah University of Science and Technology, 2019-2021
	\item \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2020}, Yandex (highly selective: only 9 winners from Russia, Belarus, Kazakhstan)}
	\item {\bf Dean's Award}, given to top students accepted to King Abdullah University of Science and Technology, 2018
	\item \textbf{Abramov’s Fund Scholarship for Excellence in Study}, Moscow Institute of Physics and Technology, 2015-2017
	\item \textbf{Asian Physics Olympiad (APhO) 2014, Honourable Mention}, Singapore (participated as a member of Russian national team)

>>>>

\section{Honors and Awards}
\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
\begin{enumerate}
	\item  \textbf{CEMSE Student Research Excellence Award}, King Abdullah University of Science and Technology, 2021
	\item \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award at FL-ICML 2021 Workshop}}
	\item \href{https://yandex.com/scholarships/#laureates}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2021}, Yandex (highly selective: only 4 winners from Russia, Belarus, Kazakhstan)}
	\item {\bf  Annual PhD progress marked as Outstanding}, King Abdullah University of Science and Technology, 2019-2021
	\item \href{https://yandex.com/scholarships/#laureates}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2020}, Yandex (highly selective: only 9 winners from Russia, Belarus, Kazakhstan)}
	\item {\bf Dean's Award}, given to top students accepted to King Abdullah University of Science and Technology, 2018
	\item \textbf{Abramov’s Fund Scholarship for Excellence in Study}, Moscow Institute of Physics and Technology, 2015-2017
	\item \textbf{Asian Physics Olympiad (APhO) 2014, Honourable Mention}, Singapore (participated as a member of Russian national team)

### 2025-11-18 CV3/general.tex
CV-ru

\section{Personal Data}

\begin{tabular}{rl}
	\textsc{Email} & \href{mailto:dakovalev1@gmail.com}{dakovalev1@gmail.com}\\
	\textsc{Website} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
	\textsc{Phone} &  +32 499 34 93 21 (Belgium)\\
	\textsc{Phone} & +7 905 719 06 98 (Russia)\\
	\textsc{Google Scholar ID} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{qHFA5z4AAAAJ}\\
	\textsc{ORCID ID} & \href{https://orcid.org/0000-0003-1467-2994}{0000-0003-1467-2994}\\
	\textsc{LinkedIn} & \href{https://www.linkedin.com/in/dakovalev1/}{dakovalev1}

@@

\section{Positions}
\begin{tabular}{rl}	
	\textsc{2023-Now}& Senior Researcher\\
	&\textbf{\href{https://research.yandex.com}{\color{black}Yandex Research}}, Moscow, Russia\\
	\textsc{2021-2023}& Research Intern\\
	&Research Center for Trusted Artificial Intelligence\\
	&\textbf{\href{https://www.ispras.ru/en/}{\color{black}Ivannikov Institute for System Programming}}, Moscow, Russia\\
	\textsc{2022-2023}& Postdoctoral Researcher\\
	& \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Université catholique de Louvain}}, Louvain-la-Neuve, Belgium\\
	\textsc{2022}& Researcher\\
	&Laboratory of Advanced Combinatorics and Network Applications\\
	&\textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia
\end{tabular}

@@

\section{Skills}

\begin{tabular}{rl}
	\textsc{Programming} & C/C++, Python,
	Algorithms and Data Structures (\href{https://codeforces.com/profile/Dakovalev1}{Codeforces master}), JAX,\\
	&PyTorch; \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, DirectX, Vulkan, HTML/CSS\\
	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
	\textsc{Computer} & macOS, LaTeX, Git\\
		\textsc{Languages} & English (Advanced), Russian (Native)
\end{tabular}

>>>>

\section{Личные данные}

\begin{tabular}{rl}
  \textsc{Электронная почта} & \href{mailto:dakovalev1@gmail.com}{dakovalev1@gmail.com}\\
  \textsc{Веб-сайт} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
  \textsc{Телефон} & +7 905 719 06 98\\
  \textsc{Google Scholar ID} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{qHFA5z4AAAAJ}\\
  \textsc{ORCID ID} & \href{https://orcid.org/0000-0003-1467-2994}{0000-0003-1467-2994}\\
  %   \textsc{LinkedIn} & \href{https://www.linkedin.com/in/dakovalev1/}{dakovalev1}

@@

\section{Опыт работы}
\begin{tabular}{rl}
  \textsc{2023-н.в.}& Ведущий исследователь\\
  &\textbf{\href{https://research.yandex.com}{\color{black}Яндекс}}, Москва, Россия\\
  \textsc{2022-2023}& Постдокторантура\\
  & \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Католический университет Лувена}}, Лувен-ла-Нёв, Бельгия\\
  \textsc{2021-2023}& Стажер-исследователь\\
  &Исследовательский центр доверенного искусственного интеллекта\\
  &\textbf{\href{https://www.ispras.ru/en/}{\color{black}Институт системного программирования им. В.П. Иванникова РАН}}
  \\&Москва, Россия\\
  \textsc{2022}& Исследователь\\
  &Лаборатория продвинутой комбинаторики и сетевых приложений\\
  &\textbf{\href{https://mipt.ru/}{\color{black}Московский физико-технический институт}}, Долгопрудный, Россия
\end{tabular}

@@

\section{Навыки}

\begin{tabular}{rl}
  \textsc{Программирование} & C/C++, Python, JAX, PyTorch,
  \\&Алгоритмы и структуры данных (\href{https://codeforces.com/profile/Dakovalev1}{Мастер Codeforces})\\
  %   \\&\textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, DirectX, Vulkan, HTML/CSS\\
  \textsc{Математика} & Математический анализ, Линейная алгебра,\\
  &Теория вероятностей и статистика, Выпуклый Анализ\\
  \textsc{Компьютер} & macOS, LaTeX, Git\\
  \textsc{Языки} & Русский, Английский
\end{tabular}

### 2025-11-18 CV3/talks.tex
CV-ru

\section{Conference Posters and Talks}
\begin{enumerate}
  \item {\bf Talk: Recent Advances in Adaptive Convex Optimization}, \href{https://icomp.cc}{\em International Conference on Computational Optimization}, Abu Dhabi, United Arab Emirates (October 2025)
  \item {\bf Talk: Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}, \href{https://ssopt.org}{\em Traditional School (Control, Information and Optimization)}, Innopolis University, Kazan, Russia (June 2025)
  \item {\bf Talk: Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}, \href{https://data-fusion.ru}{\em Data Fusion 2025 Conference}, Moscow, Russia (April 2025)
  \item {\bf Talk: Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks}, {\em Rising Stars in AI Symposium 2022}, King Abdullah University of Science and Technology, Thuwal, Saudi Arabia (March 2022)
  \item {\bf Talk/Poster: Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks}, {\em NeurIPS 2021}, Online (December 2021)
  \item {\bf Talk/Poster: Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks}, {\em International Workshop on Federated Learning for User Privacy and Data Confidentiality in Conjunction with ICML 2021}, Online (July 2021)
  \item {\bf Talk/Poster: ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks}, {\em ICML 2021}, Online (July 2021)
  \item {\bf Poster: ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks}, {\em Optimization Without Borders Conference}, Sirius University, Sochi, Russia (July 2021)
  \item {\bf Talk/Poster: A Linearly Convergent Algorithm for Decentralized Optimization: Sending Less Bits for Free!}, {\em AISTATS 2021}, Online (April 2021)
  \item {\bf Poster: Linearly Converging Error Compensated SGD}, {\em NeurIPS 2020}, Online (December 2020)
  \item {\bf Talk/Poster: Optimal and Practical Algorithms for Smooth and Strongly Convex Decentralized Optimization}, {\em NeurIPS 2020}, Online (December 2020)
  \item {\bf Talk: Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems}, {\em ICML 2020}, Online (July 2020)
  \item {\bf Poster: RSN: Randomized Subspace Newton}, {\em NeurIPS 2019}, Vancouver, Canada (December 2019)
  \item {\bf Poster: Stochastic Proximal Langevin Algorithm: Potential Splitting and Nonasymptotic Rates}, {\em NeurIPS 2019}, Vancouver, Canada (December 2019)
  \item {\bf Talk: Revisiting Stochastic Extragradient Method}, {\em International Conference on Continuous Optimization 2019}, Technical University, Berlin, Germany (August 2019)
  \item {\bf Poster: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Data Science Summer School 2019}, Ecole Polytechnique, Paris, France (June 2019)
  \item {\bf Poster: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, \href{https://ssopt.org}{\em Traditional School (Control, Information and Optimization)}, Higher School of Economics Study Center, Voronovo, Russia (June 2019)
  \item {\bf Talk: Stochastic Spectral Descent Methods}, {\em Automatic control and Optimization Theory Weekly Seminar}, Institute for Control Problems, Moscow, Russia (March 2019)
  \item {\bf Talk: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Modern Optimization Methods Seminar}, Moscow Institute of Physics and Technology, Moscow, Russia (March 2019)
  \item {\bf Poster: Stochastic Spectral Descent Methods}, {\em NeurIPS 2018}, Montreal, Canada (December 2018)
  \item {\bf Poster: Stochastic Spectral Descent Methods}, {\em Optimization and Big Data Workshop}, King Abdullah University of Science and Technology, Thuwal, Saudi Arabia (June 2018)
  \item {\bf Poster: Stochastic Spectral Descent Methods}, \href{https://ssopt.org}{\em Traditional School (Control, Information and Optimization)}, Higher School of Economics Study Center, Voronovo, Russia (February 2018)
\end{enumerate}

>>>>

\section{Conference Posters and Talks}
\begin{enumerate}
  \item {\bf Talk: Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}, {\em Traditional School (Control, Information and Optimization)}, Innopolis University, Kazan, Russia (June 2025)
  \item {\bf Talk: Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}, {\em Data Fusion 2025 Conference}, Moscow, Russia (April 2025)
  \item {\bf Talk: Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks}, {\em Rising Stars in AI Symposium 2022}, King Abdullah University of Science and Technology, Thuwal, Saudi Arabia (March 2022)
  \item {\bf Talk/Poster: Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks}, {\em NeurIPS 2021}, Online (December 2021)
  \item {\bf Talk/Poster: Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks}, {\em International Workshop on Federated Learning for User Privacy and Data Confidentiality in Conjunction with ICML 2021}, Online (July 2021)
  \item {\bf Talk/Poster: ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks}, {\em ICML 2021}, Online (July 2021)
  \item {\bf Poster: ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks}, {\em Optimization Without Borders Conference}, Sirius University, Sochi, Russia (July 2021)
  \item {\bf Talk/Poster: A Linearly Convergent Algorithm for Decentralized Optimization: Sending Less Bits for Free!}, {\em AISTATS 2021}, Online (April 2021)
  \item {\bf Poster: Linearly Converging Error Compensated SGD}, {\em NeurIPS 2020}, Online (December 2020)
  \item {\bf Talk/Poster: Optimal and Practical Algorithms for Smooth and Strongly Convex Decentralized Optimization}, {\em NeurIPS 2020}, Online (December 2020)
  \item {\bf Talk: Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems}, {\em ICML 2020}, Online (July 2020)
  \item {\bf Poster: RSN: Randomized Subspace Newton}, {\em NeurIPS 2019}, Vancouver, Canada (December 2019)
  \item {\bf Poster: Stochastic Proximal Langevin Algorithm: Potential Splitting and Nonasymptotic Rates}, {\em NeurIPS 2019}, Vancouver, Canada (December 2019)
  \item {\bf Talk: Revisiting Stochastic Extragradient Method}, {\em International Conference on Continuous Optimization 2019}, Technical University, Berlin, Germany (August 2019)
  \item {\bf Poster: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Data Science Summer School 2019}, Ecole Polytechnique, Paris, France (June 2019)
  \item {\bf Poster: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Traditional School (Control, Information and Optimization)}, Higher School of Economics Study Center, Voronovo, Russia (June 2019)
  \item {\bf Talk: Stochastic Spectral Descent Methods}, {\em Automatic control and Optimization Theory Weekly Seminar}, Institute for Control Problems, Moscow, Russia (March 2019)
  \item {\bf Talk: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Modern Optimization Methods Seminar}, Moscow Institute of Physics and Technology, Moscow, Russia (March 2019)
  \item {\bf Poster: Stochastic Spectral Descent Methods}, {\em NeurIPS 2018}, Montreal, Canada (December 2018)
  \item {\bf Poster: Stochastic Spectral Descent Methods}, {\em Optimization and Big Data Workshop}, King Abdullah University of Science and Technology, Thuwal, Saudi Arabia (June 2018)
  \item {\bf Poster: Stochastic Spectral Descent Methods}, {\em Traditional School (Control, Information and Optimization)}, Higher School of Economics Study Center, Voronovo, Russia (February 2018)
\end{enumerate}
